---
title: "Bay Area useR Group - Time Series Workshop - ARIMA"
subtitle: ""
date: "2019-10-05"
author:
  - name: "Rami Krispin"
    url: http://twitter.com/rami_krispin
  - name: "Danton Noriega"
    url: http://twitter.com/dantonnoriega
output: 
  distill::distill_article:
    toc: true
    toc_float: true
    toc_depth: 3
editor_options: 
  chunk_output_type: console
---

<style type="text/css">

body{ /* Normal  */
      font-size: 20px;
  }
td {  /* Table  */
  font-size: 16px;
}
h1.title {
  font-size: 38px;
  color: Black;
}
h1 { /* Header 1 */
  font-size: 28px;
  color: #468cc8;
}
h2 { /* Header 2 */
    font-size: 30px;
  color: #468cc8;
}
h3 { /* Header 3 */
  font-size: 25px;
  color: #468cc8;
}

h4 { /* Header 4 */
  font-size: 20px;
  color: #81A4BE;
}

h5 { /* Header 4 */
  color: #81A4BE;
}

d-code { /* Code block */
    background-color: #f9f9f9;
}

code { /* Code block */
    font-size: 16px;
    color: #be8181;
    background-color: #f5f5f5;
    font-family: "Courier";
}
pre.text-output { /* Code block - determines code spacing between lines */
    font-size: 14px;
    background-color: #ecf6ff;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=9, fig.height=5, warning=FALSE, message=FALSE, layout="l-body-outset", out.extra="class=external")
```


```{r arima-child, child = "time-series-workshop-arima.Rmd"}
```
